---
title: "Histogram"
output: html_notebook

---

## Numeric
- histogram (1)
- scatter plot (2)
## discrete numeric variable (numeric var divided into category)
- barplot
## category/factor
- Barplot (1)

## x=Category/factor and  y=numberic
- boxplot

manufacturer: chr [1:234] "audi" "audi" "audi" "audi" ...
 $ model       : chr [1:234] "a4" "a4" "a4" "a4" ...
 $ displ       : num [1:234] 1.8 1.8 2 2 2.8 2.8 3.1 1.8 1.8 2 ...
 $ year        : int [1:234] 1999 1999 2008 2008 1999 1999 2008 1999 1999 2008 ...
 $ cyl         : int [1:234] 4 4 4 4 6 6 6 4 4 4 ...
 $ trans       : chr [1:234] "auto(l5)" "manual(m5)" "manual(m6)" "auto(av)" ...
 $ drv         : chr [1:234] "f" "f" "f" "f" ...
 $ cty         : int [1:234] 18 21 20 21 16 18 18 18 16 20 ...
 $ hwy         : int [1:234] 29 29 31 30 26 26 27 26 25 28 ...
 $ fl          : chr [1:234] "p" "p" "p" "p" ...
 $ class       : Factor w/ 7 levels "2seater","compact",..

```{r}
library(ggplot2)
```

dataset from ggplot2 library
```{r}
df <- ggplot2::mpg
```

```{r}
head(df)
```

```{r}
df$class <- factor(df$class)
```

#### histogram 
- [base histogram](https://r-coder.com/histogram-r/)
base R histogram

```{r}
graphics::hist(df$hwy, breaks = "sturges", col = "#00BFC4",
xlab = "Highway miles per gallon",
main = "Histogram in base R")
```
breaks can be set to number 

```{r}
graphics::hist(df$hwy, breaks = 27, col = "#00BFC4",
xlab = "Highway miles per gallon",
main = "Histogram in base R")
```

```{r}
graphics::hist(df$displ, breaks = "sturges", col = "#00BFC4",
      xlab = "Engine Displacement in Liter",
      main = "Histogram in base R")
```

2 variables in one hist plot
```{r}
graphics::hist(df$hwy, breaks = "sturges", col = "#00BFC4",
xlab = "Highway miles per gallon",
main = "Histogram in base R")
hist(df$cty, add = TRUE, col = "#F8766D")
```

```{r}
histDenNorm <- function(x, main = "") {
   hist(x, prob = TRUE, main = main) # Histogram
   lines(density(x), col = "blue", lwd = 2) # Density 
   x2 <- seq(min(x), max(x), length = 40)
   f <- dnorm(x2, mean(x), sd(x))
   lines(x2, f, col = "red", lwd = 2) # Normal
   legend("topright", c("Histogram", "Density", "Normal"), box.lty = 0,
          lty = 1, col = c("black", "blue", "red"), lwd = c(1, 2, 2))
}
```

```{r}
histDenNorm(df$hwy)
```

ggplot histogram

```{r}
ggplot(data = df, aes(x = hwy)) +
geom_histogram(bins = 7, fill = "#00BFC4", color = "#ffffff")
```

```{r}
nbreaks <- pretty(range(df$hwy), n = nclass.Sturges(df$hwy),
                  min.n = 1)
ggplot(data = df, aes(x = hwy)) +
geom_histogram(breaks = nbreaks, fill = "#00BFC4", color = "#000000")
```

with geom_bar and scale_x_binned
```{r}
ggplot(data = df, aes(x = hwy)) +
geom_bar(fill = "#00BFC4", color = "#ffffff") +
scale_x_binned()
```

```{r}
ggplot(diamonds, aes(price, fill = cut)) +
  geom_histogram(binwidth = 500)
```

